%----------- EXPERIENCE SECTION -----------%

\section{Experience}
\vspace{2pt}
\resumeSubHeadingListStart

%-----------------------------------------
% EXL: Engagement Manager
%-----------------------------------------
\experienceEntry
{EXL}
{February 2024 -- Present}
{Engagement Manager(Technical Program \& Delivery Lead)}
{Bangalore}

\highlightsTwoArgs
{Forward Deployed Engineering Manager }
{Driving GenAI innovation, P\&L, and people strategy}

\experienceDetails{Commercial Strategy \& Account Growth}{
    \item \small Owned P\&L and commercial margins for the account. Created business cases and ROI models, securing a \$500K R\&D investment for GenAI adoption—driving vertical expansion and a 30\% revenue uplift within 9 months.
}

\experienceDetails{Executive Stakeholder Management}{
    \item \small Managed C-Suite and VP relationships using quarterly SteerCos and data-driven QBRs. Translated technical constraints into value narratives to ensure renewals and long-term partnership health.
}

\experienceDetails{GenAI Architecture \& Builder Leadership}{
    \item \small Architected an enterprise-grade Agentic AI Data Quality Platform. Designed multi-agent workflows and RAG pipelines (BigQuery VectorStore / Vertex AI) enabling autonomous anomaly detection and reducing ticket resolution time by 50\%.
}

\experienceDetails{Program Governance \& Risk Management}{
    \item \small Orchestrated 5+ concurrent global workstreams. Established governance using RAID logs, quality gates, and release planning to control scope and ensure 100\% on-time delivery.
}

\experienceDetails{Platform Engineering}{
    \item \small Directed the Clean Room migration of sensitive data from BigQuery to Snowflake. Implemented Snowpipe-based ELT and privacy governance to securely integrate 1st/3rd party datasets.
}

\vspace{5pt}

%-----------------------------------------
% EXL: Project Manager
%-----------------------------------------
\experienceEntry
{EXL}
{January 2022 -- January 2024}
{Project Manager (Data Platforms \& MLOps)}
{Bangalore}

\highlightsTwoArgs
{Business development}
{Fast-track promotion in 2 years}

\experienceDetails{Org Building \& People Leadership}{
    \item \small Led a 14-member cross-functional team (DE, MLE, Full-Stack). Created competency matrices, structured onboarding, and career coaching—achieving 95\% retention and reducing hiring cycle time by 30\%.
}

\experienceDetails{Technical Program Delivery}{
    \item \small Led Agile (Scrum) delivery for a multi-tenant Airflow-on-GKE platform processing 1TB+ daily data. Managed SOWs and technical dependencies to achieve 95\% SLA adherence and reduce operational overhead by 30\%.
}

\experienceDetails{MLOps \& SDLC Implementation}{
    \item \small Defined ML SDLC and managed 15+ production models (CLV, Reactivation) using Vertex AI and MLflow. Created a reusable pilot-to-production framework improving release velocity.
}

\experienceDetails{Security Automation}{
    \item \small Built an IAM provisioning system (Python/FastAPI + Retool) automating access workflows across GCP/AWS and reducing access turnaround time by 40\%.
}

\vspace{5pt}

%-----------------------------------------
% EXL: Assistant Project Manager
%-----------------------------------------
\experienceEntry
{EXL}
{June 2020 -- December 2021}
{Assistant Project Manager (Data Engineering)}
{Bangalore}

\highlightsThreeArgs
{US media \& telecom conglomerate}
{OTT space}
{Fast-track promotion in 1.5 years}

\experienceDetails{Pipeline Modernization}{
    \item \small Migrated on-prem ETL workloads to cloud-native GCP + Airflow. Optimized DAGs to reduce data latency by 25\% with zero downtime.
}

\experienceDetails{Operational Excellence}{
    \item \small Built Python-based monitoring frameworks providing real-time visibility and maintaining a 95\%+ job success rate.
}

\experienceDetails{Stakeholder Enablement}{
    \item \small Translated technical insights into strategic recommendations for senior leadership, improving productivity by 10\%.
}

\vspace{5pt}

%-----------------------------------------
% Amazon: Program Manager Intern
%-----------------------------------------
\experienceEntry
{Amazon}
{April 2019 -- May 2019}
{Program Manager Intern (Operations Analytics)}
{Hyderabad}

\highlightsTwoArgs
{Streamlined packaging across India transportation network}
{Reduced unloading time by 1100 hours/week}

\experienceDetails{Process Optimization}{
    \item \small Analyzed 37M+ records to identify bottlenecks. Built SQL-driven anomaly detection improving process efficiency—saving 1,100 labor hours/week and reducing damages by 65\%.
}

\vspace{5pt}

%-----------------------------------------
% UnitedHealth Group: Software Engineer
%-----------------------------------------
\experienceEntry
{UnitedHealth Group}
{July 2015 -- June 2018}
{Software Engineer (Big Data \& Analytics)}
{Bangalore}

\highlightsTwoArgs
{SME for two \$400K+ projects}
{Fast-track promotion in 8 months}

\experienceDetails{Process Improvement}{
    \item \small Built real-time reporting apps reducing manual effort by 60\% and improving SLA compliance to 90\%.
    \item \small Analyzed 100GB+/week healthcare data delivering insights that boosted SLA adherence by 15\% YoY.
}

\experienceDetails{Big Data Engineering \& Analytics}{
    \item \small Migrated legacy systems to big data stack, improving performance by 500\% via optimized architecture.
    \item \small Designed Spark-Scala algorithms to process unstructured data, improving usability by 35\%.
    \item \small Built custom compression solutions reducing storage costs by 20\% and improving query speeds.
}

\resumeSubHeadingListEnd
